---
title: "Quantitative Methods Series"
subtitle: " Session 01 "
author: "M. Bisiada, G. Boleda, T. Brochhagen"
output:
  html_document: default
urlcolor: blue
---

# Pre-session tasks
We will use the [programming language R](https://www.r-project.org/). You do not need to have programmed neither in R nor any other language before. However, you should have access to a machine that can run R code to get the most out of this class. Additionally, we also recommend installing [RStudio](https://rstudio.com/). This is a graphical interface that allows you to manipulate R code & data more easily. You don't strictly need it, but chances are it's going to make your quantitative life easier.

## Task 1: Install R and RStudio

The details of how to install R and RStudio depend on your operating system. [This Datacamp tutorial](https://www.datacamp.com/community/tutorials/installing-R-windows-mac-ubuntu) gives a detailed description on how to do so for Windows, Mac OS X, and Ubuntu.

## Task 2: Test installation 
Make sure your installation was successful. 

One way to do so is to [download this page's markdown](https://quantitativemethods.github.io/2020q2/session01.Rmd); open it in RStudio; and press the green "play"-button to the right of the grey box just below this text. That tells Rstudio to run the code inside the box.

```{r}
print('Welcome to the Quantitative Methods Series')

#A demonstration of R code (to see that the code is running)
x <- 2 #this assigns the value '2' to variable 'x'
y <- 5 #this assigns the value '5' to variable 5

#Running this box of code will print the result of these operations:
x+y 
x*y
x**y
```

You can play around with this interactive document as much as you want. That's why we're making it available. For each session, you can find:

  * the Rmarkdown source <img src="../fa/markdown-brands.svg" width="35"/>
  * just the R code (without the text) <img src="../fa/r-project-brands.svg"  width="35"/>

***

# Session overview

  1. Introduction to this series and general overview
  2. Get to know each other('s statistical needs)
  3. Troubleshoot issues, if any, concerning the pre-session tasks
  4. Reading in data
  
  
## 1. Introduction and general overview
... a little bit about what we want to do...

## 2. Get to know each other('s statistical needs)

## 3. Troubleshooting

## 4. Reading data

```{r setup, warning=FALSE, message=FALSE}
library(dplyr)

```


***
```{r}
sessionInfo()
```
